### 2019-04-08 manuscript.tex
Update manuscript.tex

\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, ShelWand11, more} and other norm studies of why mother cut daughters etc}

@@

- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
- \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}

- community level of effects -

- tipping point/threshold -

@@

- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} .

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.)

@@

==================================
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}

--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination,” for marital market.  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

% Comparison of individual vs. village contribution to the variation of women’s fgc status to fgc future (see Fig 2 https://www.sciencedirect.com/science/article/pii/S0304387815000620#bb0230)

OVERALL:
% “Many girls who are cut are daughters of women who oppose the practice” (\cite{UNIC13})
% Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms \cite{PashPonn16}. It implied that community norm (social norm) was not as clear as suggested \cite{EffeVogt15}, but believed otherwise \cite{DuncWand11, Hayf06, Mack96, Mack00, Mack06, Youn02} (to confirm).

— Second interpretation —
--- socio demographic interpretation at both levels (link this to modernization?)
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{KarmKand11}

— by nations —
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
1. comparison: \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

---- Sierra Leon: 
\cite{ShelHern06, ShelHern13}  (Are they on Senegal or Sierra Leone?)

% FGC laws in those nations

@@

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% put religion into consideration of our findings (i.e., national distribution of religion, how many muslins in each country)
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}
% \cfcmt{the structure:  cultural and legal background; comparison of our findings to previous studies; implications}
% Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status \cit{Hayf05}

@@

% To question the difference between MC and FGC if FGC can be minimized to the form of “just a knick” or type I or minor.

@@

(There are also studies proposing various factors impacting FGC practices, such as women's education \cite{KandNwak09,VanMeek15}, social economic status \cite{} etc, community levels of influences.) (What is conventional in convention theory can also be focal points to gender awareness and modern development.  Question:  What is the differences between convention theory and community level of impact on FGC? the same or?)

% To compare with findings in Burkina Faso \cite{KarmKand11}, and Tostan

@@

% Latikin 1995:  Norms o unsafe behaviours are not trivially changed trough information.
% Beliefs are susceptible social confirmation (Centola)
% Small world and "hubs" accelerate diseases but slow down behaviours change (Centola)
% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)

\cite{EffeVoge15}:  Each family may have its own threshold of fgc. I think fgc norm has shifted from marraige advantage of social capital of social networking as proposed by Shell-Duncon and her colleagues \cite{ShelWand11}.  To elaborate the shifted values of fgc, what it imply and how to apply the change to policy.

@@

\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."

>>>>

\cfonly{add \cite{AlcaGonz13, BellNova15, PashPonn16, Rima08, ShelWand11, more} and other norm studies of why mother cut daughters etc}

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}. “alternative convention/peer convention\cite{ShelWand11}
 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}
\cite{PashPonn16}: Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms

- community level of effects -
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
- tipping point/threshold -

@@

- modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02}. 
 \cit{Hayf05}  Wealth:  Some research showed that household wealth has nonlinear correlation with women's FGC status predictor of daughter's FGC status
\cite{KandNwak09,VanMeek15} proposing various factors impacting FGC practices, such as women's education

\cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{KarmKand11}

— Suggestions —
- empowering community, engaging community leaders and other strategies \citeBergDeni13b}
- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}

@@

==================================
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm),

--- attitudes vs. norm (beliefs) vs. (behavioural) intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intention:  attitude, norm and perceived behavioroal control.

\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

OVERALL:
\cite{UNIC13}:  “Many girls who are cut are daughters of women who oppose the practice”

— by nations and laws in those nations—
---- Kenya: legal background:  Kenya \cite{GKEN01}; \cite{UNIC13}; 
 vs. \cite{Chia14, Hayf05}, and [\url{http://kenya.usaid.gov/programs/women/182 PEPFAR/kenya}]
---- Mali: ``The occurrence of FGM/C is also concentrated in certain West African countries where prevalence rates range from 72–96 percent: Burkina Faso, the Gambia, Guinea, and Mali. The populations of these countries share certain social and historical ties, which suggests that a strategy to eliminate FGM/C in one of these countries might be successful in others. FGM/C is practiced as part of the initiation into a secret society in Liberia and Sierra Leone. We should expect that the repercussions for mothers there who do not send their daughters to be initiated would be different than for mothers in nearby Mali or Guinea \cite{YodaWang13}

@@

---- Sierra Leone: 
\cite{Sagn14}

@@

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}

@@

@@

@@

% Latikin 1995:  Norms o unsafe behaviours are not trivially changed trough information.
% Beliefs are susceptible social confirmation (Damon Centola)
% a chart to show changes of FGC prevalence from 2000 to the current surveys (Kenya 98, 03; Nigeria 99, 03; Mali 01, 06?  (see \cite{BoylCorl10}, table 1)

\cite{EffeVoge15}:  Each family may have its own threshold of fgc. I think fgc norm has shifted from marraige advantage of social capital of social networking as proposed by Shell-Duncon and her colleagues \cite{ShelWand11}.  To elaborate the shifted values of fgc, what it imply and how to apply the change to policy.
\cite{CentBeck18}:  social convention and tipping point

@@
